---
title: "RESS20Mar2023"
output: beamer_presentation
date: "2023-03-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("stats")
library("Rgraphviz")
#install.packages("hrbrthemes")
#BiocManager::install("Rgraphviz")
library("fitdistrplus")
library("bnlearn")
library("readxl")
library("hdrcde")
library(gRain)
library(stringi)
library("greekLetters")
library(ggplot2)
library(dplyr)
library(hrbrthemes)
```

## Simulation in Python

The Python files are provided in the folder at ...


## Reading CSV files

Here is the code for reading csv files as data-frames:


```{r chunk0001, echo = TRUE}
rm(list=ls())
#setwd("C://Users//20204066//Box//RESS-format//2022Dec10-RunFullmodel//18December2022SSBN4RYesting//")
getwd()
Road_cond_tables<-read.csv("conditional_prob_table_road_level_concate01.csv",sep = ",",2)
Subset_cond_tables<-read.csv("conditional_prob_table_road_to_subnet_level_concate01.csv",sep = ",",2)
System_cond_tables<-read.csv("conditional_prob_table_system_level.csv", sep=",",2)
```


With probability 0.6 is the first element of ordered "Maint_rate_IndepenVarLvel_uniq", and 0.4 the other element.



```{r chunk00015, echo = TRUE}
Bridge_road_list<-unique(Road_cond_tables$IndepenVar)
BNString<-""
BNString22<-""
CPString<-""
Bridge_lists_all<-list()

ii_end<-length(Bridge_road_list)
for (ii in 1:ii_end){
  if (nchar(Bridge_road_list[ii]) > 1)
    {
    BNString<-paste0(BNString, "[", paste(Bridge_road_list[ii],sep = "") ,"]")
    DepenVar<-Road_cond_tables[Road_cond_tables$IndepenVar==Bridge_road_list[ii],"DepenVar"]
    DepenVar_list<-unique(DepenVar)
    #for (jj in 1:length(DepenVar_list)){
    #  BNString22<-paste0(BNString22, "[", paste(DepenVar_list[jj],sep = "") , "|", paste(Bridge_road_list[ii],sep     # = "")  ,"]")}
    
      
    Bridge_lists_all<-append(Bridge_lists_all,Bridge_road_list[ii])
    
    
    Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$IndepenVar==Bridge_road_list[ii],"IndepenVarLvel"]
    Maint_rate_IndepenVarLvel_uniq<-sort(unique(Maint_rate_IndepenVarLvel))
    Maint_rate_IndepenVarLvel_uniq_index<-seq_along(Maint_rate_IndepenVarLvel_uniq)
    str2<-paste(Bridge_road_list[ii],sep = "")
  
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Maint_rate_IndepenVarLvel_uniq_index"))))

      
    assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(c(0.6, 0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq_index))"))) )
  
    
    
    CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))
    
    }
}



Bridge_road_list<-unique(Road_cond_tables$IndepenVar1)
ii_end<-length(Bridge_road_list)
for (ii in 1:ii_end){
  if (nchar(Bridge_road_list[ii]) > 1)
    {
    BNString<-paste0(BNString, "[", paste(Bridge_road_list[ii],sep = "") ,"]")
    DepenVar<-Road_cond_tables[Road_cond_tables$IndepenVar1==Bridge_road_list[ii],"DepenVar"]
    DepenVar_list<-unique(DepenVar)

    
    
    
    Bridge_lists_all<-append(Bridge_lists_all,Bridge_road_list[ii])
    
    
    Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$IndepenVar1==Bridge_road_list[ii],"IndepenVar1Lvel"]
    Maint_rate_IndepenVarLvel_uniq<-sort(unique(Maint_rate_IndepenVarLvel))
    Maint_rate_IndepenVarLvel_uniq_index<-seq_along(Maint_rate_IndepenVarLvel_uniq)
    str2<-paste(Bridge_road_list[ii],sep = "")
  
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Maint_rate_IndepenVarLvel_uniq_index"))))
  
    assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(c(0.6, 0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq_index))"))) )

    

    
    CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))

              
    }
}





Bridge_road_list<-unique(Road_cond_tables$IndepenVar2)
ii_end<-length(Bridge_road_list)
for (ii in 1:ii_end){
  if (nchar(Bridge_road_list[ii]) > 1)
    {
    BNString<-paste0(BNString, "[", paste(Bridge_road_list[ii],sep = "") ,"]")
    DepenVar<-Road_cond_tables[Road_cond_tables$IndepenVar2==Bridge_road_list[ii],"DepenVar"]
    DepenVar_list<-unique(DepenVar)

    
    
    Bridge_lists_all<-append(Bridge_lists_all,Bridge_road_list[ii])
    
    
    Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$IndepenVar2==Bridge_road_list[ii],"IndepenVar2Lvel"]
    Maint_rate_IndepenVarLvel_uniq<-sort(unique(Maint_rate_IndepenVarLvel))
    Maint_rate_IndepenVarLvel_uniq_index<-seq_along(Maint_rate_IndepenVarLvel_uniq)
    str2<-paste(Bridge_road_list[ii],sep = "")
  
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Maint_rate_IndepenVarLvel_uniq_index"))))
  
    assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(c(0.6, 0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq_index))"))) )
    # array(Maint_rate_IndepenVarLvel_uniq 

    CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))
        
      
    }
}









```



## Continue

```{r chunk00016, echo = TRUE}



Raod_list_BNString<-unique(Road_cond_tables$DepenVar)
for (ii in 1:length(Raod_list_BNString)){
    IndepenVar<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Raod_list_BNString[ii],"IndepenVar"])
    IndepenVar1<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Raod_list_BNString[ii],"IndepenVar1"])
    IndepenVar2<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Raod_list_BNString[ii],"IndepenVar2"])

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Raod_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1){  
    BNString22<-paste0(BNString22, "[", paste(Raod_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,sep = "")  ,"]")
    
    }
    else {
    BNString22<-paste0(BNString22, "[", paste(Raod_list_BNString[ii],sep = "") , "|", paste(IndepenVar,sep = "")  ,"]")
      
    }
  }


Road_list<-unique(Road_cond_tables$DepenVar)
Road_lists_all<-list()


for (ii in 1:length(Road_list)){
  if (nchar(Road_list[ii]) > 1)
    {

    #BNString<-paste0(BNString, "[", paste(Road_list[ii],sep = "") ,"]")
    Road_lists_all<-append(Road_lists_all,Road_list[ii])
    
    
    Road_cond_prob<-Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"CondProb"]
    Road_levels_list<-Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"DepenVarLvel"]
    Road_levels_list_index<-seq_along(unique(Road_levels_list))
    Road_levels_list_num<-length(unique(Road_levels_list))
    

    IndepenVar<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar"])
    IndepenVar_uniq_num<-length(unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVarLvel"]))
    IndepenVar1<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar1"])
    IndepenVar1_uniq_num<-length(unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar1Lvel"]))
    IndepenVar2<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar2"])
    IndepenVar2_uniq_num<-length(unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar2Lvel"]))

        
    str2<-paste(Road_list[ii],sep = "")
    str3<-paste(IndepenVar,"=",IndepenVar,"_range",sep = "")
    str4<-paste(IndepenVar1,"=",IndepenVar1,"_range",sep = "")
    str5<-paste(IndepenVar2,"=",IndepenVar2,"_range",sep = "")

    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Road_levels_list_index"))))
    
    #cat(IndepenVar2_uniq_num,'IndepenVar2_uniq_num')

        

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){

      # rr<-paste("arrayRoad_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,str4,str5,"))")
      #print(rr)
      
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Road_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,",",str4,",",str5,"))"))) )
    }
        

    else if (nchar(IndepenVar1) > 1){

      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Road_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,",",str4,"))"))) )
    }
     else {
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Road_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,"))"))) )
       
     }   

    if (ii <=length(Road_list) ){
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))}
    else {
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob',sep=""))
    }
    
    }
}




```


Read and create subnet file..

```{r chunk00017, echo = TRUE}
BNString22
Subnet_list_BNString<-unique(Subset_cond_tables$DepenVar)
for (ii in 1:length(Subnet_list_BNString)){

    IndepenVar<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar"])
    IndepenVar1<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar1"])
    IndepenVar2<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar2"])
    IndepenVar3<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar3"])

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1  & nchar(IndepenVar3) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,":",IndepenVar3,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1){  
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,sep = "")  ,"]")
    
    }
    else {
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,sep = "")  ,"]")
      
    }
  }




Subnet_list<-unique(Subset_cond_tables$DepenVar)
Subnet_lists_all<-list()



for (ii in 1:length(Subnet_list)){
  if (nchar(Subnet_list[ii]) > 1  )
    {

    #BNString<-paste0(BNString, "[", paste(Road_list[ii],sep = "") ,"]")
    Subnet_lists_all<-append(Subnet_lists_all,Subnet_list[ii])
    
    
    Subnet_cond_prob<-Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"CondProb"]
    Subnet_levels_list<-Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"DepenVarLvel"]
    Subnet_levels_list_index<-seq_along(unique(Subnet_levels_list))
    Subnet_levels_list_num<-length(unique(Subnet_levels_list))
    

    

    IndepenVar<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar"])
    IndepenVar_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVarLvel"]))
    IndepenVar1<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar1"])
    IndepenVar1_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar1Lvel"]))
    IndepenVar2<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar2"])
    IndepenVar2_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar2Lvel"]))
    IndepenVar3<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar3"])
    IndepenVar3_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar3Lvel"]))

        
    str2<-paste(Subnet_list[ii],sep = "")
    str3<-paste(IndepenVar,"=",IndepenVar,"_range",sep = "")
    str4<-paste(IndepenVar1,"=",IndepenVar1,"_range",sep = "")
    str5<-paste(IndepenVar2,"=",IndepenVar2,"_range",sep = "")
    str6<-paste(IndepenVar3,"=",IndepenVar3,"_range",sep = "")
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Subnet_levels_list_index"))))

    #cat("    %%%%%%%%%%  ",ii)
    #cat("::::", IndepenVar_uniq_num, IndepenVar1_uniq_num, Subnet_levels_list_num)
    #cat("uuuuuuuuuuu")
    

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1 & nchar(IndepenVar3) > 1){

     # rr<-paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,",",str6,"))")
      # print(rr)

            
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num,IndepenVar3_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,",",str6,"))"))) )
    }

    else if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){

      # rr<-paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,"))")
      # print(rr)

            
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,"))"))) )
    }
        

    else if (nchar(IndepenVar1) > 1){

      #rr<-paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,"))")
      #print(rr)
      
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,"))"))) )
    }
     else {
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,"))"))) )
       
     }   

    if (ii <=length(Subnet_list) ){
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))}
    else {
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob',sep=""))
    }
    
    }
}




```



system nodes and conditional probs

```{r chunk00018, echo = TRUE}

Sys_list_BNString<-unique(System_cond_tables$DepenVar)

for (ii in 1:length(Sys_list_BNString)){
    IndepenVar<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar"])
    IndepenVar1<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar1"])
    IndepenVar2<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar2"])
    IndepenVar3<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar3"])

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1  & nchar(IndepenVar3) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,":",IndepenVar3,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1){  
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,sep = "")  ,"]")
    
    }
    else {
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,sep = "")  ,"]")
      
    }
  }



System_var_list<-unique(System_cond_tables$DepenVar)
System_var_lists_all<-list()


for (ii in 1:length(System_var_list)){
  if (nchar(System_var_list[ii]) > 1  )
    {

    #BNString<-paste0(BNString, "[", paste(Road_list[ii],sep = "") ,"]")
    System_var_lists_all<-append(System_var_lists_all,System_var_list[ii])
    
    
    System_cond_prob<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"CondProb"]
    System_var_levels_list<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"DepenVarLvel"]
    System_var_levels_list_index<-seq_along(unique(System_var_levels_list))
    System_var_levels_list_num<-length(unique(System_var_levels_list))
    
    IndepenVar_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVarLvel"]))
    IndepenVar1_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar1Lvel"]))
    IndepenVar2_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar2Lvel"]))
    IndepenVar3_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar3Lvel"]))

    

    IndepenVar<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar"])
    IndepenVar1<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar1"])
    IndepenVar2<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar2"])
    IndepenVar3<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar3"])

        
    str2<-paste(System_var_list[ii],sep = "")
    str3<-paste(IndepenVar,"=",IndepenVar,"_range",sep = "")
    str4<-paste(IndepenVar1,"=",IndepenVar1,"_range",sep = "")
    str5<-paste(IndepenVar2,"=",IndepenVar2,"_range",sep = "")
    str6<-paste(IndepenVar3,"=",IndepenVar3,"_range",sep = "")

    #cat("    %%%%%%%%%%  ",ii)
    #cat("::::", IndepenVar_uniq_num, IndepenVar1_uniq_num, Subnet_levels_list_num)
    #cat("uuuuuuuuuuu")
    


    rr<-paste("array(System_cond_tables, dim = c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num ), dimnames = list(",str2,"= System_var_levels_list_index,",str3,",",str4,",",str5,",",str6,"))")
    print(rr)

            
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(System_cond_prob, dim = c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num,IndepenVar3_uniq_num ), dimnames = list(",str2,"= System_var_levels_list_index,",str3,",",str4,",",str5,",",str6,"))"))) )

    if (ii <length(System_var_list) ){
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))}
    else {
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob',sep=""))
    }
    
    }
}


# System_cond_prob<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[1],"CondProb"]
# System_var_levels_list<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[1],"DepenVarLvel"]
# System_var_levels_list_index<-seq_along(unique(System_var_levels_list))
# System_var_levels_list_num<-length(unique(System_var_levels_list))
# 
# System_var_levels_list_index
# c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num )
# list( TotalCostDisc11 = System_var_levels_list_index, Subnet0Costs=Subnet0Costs_range , Subnet1Costs=Subnet1Costs_range , Subnet2Costs=Subnet2Costs_range , Subnet3Costs=Subnet3Costs_range )
# tte<-array(System_cond_tables, dim = c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num ), dimnames = list( TotalCostDisc11 = System_var_levels_list_index, Subnet0Costs=Subnet0Costs_range , Subnet1Costs=Subnet1Costs_range , Subnet2Costs=Subnet2Costs_range , Subnet3Costs=Subnet3Costs_range ))


```




Creat BN model

```{r chunk00019, echo = TRUE}
CPString#<-"Bridge0Road13=Bridge0Road13_prob,Road13Avail=Road13Avail_prob"
assign(as.vector(paste('cpt',sep="")),eval(parse(text=paste("list(",CPString,")"))) )
cpt
BNString22

#BNStringAll<-paste0("[Bridge0Road13]",BNString22,"")
BNStringAll<-paste0(BNString,BNString22,"")
BNStringAll
BNLayerOneTime = model2network(BNStringAll)
cpt


bn11 = custom.fit(BNLayerOneTime, cpt)



graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")

graphviz.plot(bn11, layout = "fdp") #circo


bn.fit.barchart(bn11$Road57Costs, main = "Subnet3Costs",
                xlab = "Pr(Subnet3Costs |..)", ylab = "")

graphviz.plot(bn11, shape = "ellipse")

#Distribution here 
sim = cpdist(bn11, nodes = "TravelTimeDisc11", n = 1000,evidence = ((Bridge0Road13 == 1) & (Bridge0Road49 == 2) & (Bridge0Road63 == 2)))
simPure <- gsub(",", "", sim$TravelTimeDisc11)   # remove comma
simPure <- as.numeric(simPure)
#hist(simPure,col="blue",freq = FALSE)
h <- hist(simPure, plot=FALSE)
h$density = h$counts/sum(h$counts) * 100
plot(h, main="Distribution of Salaries",
     xlab="Salary ($K)",
     ylab="Percent",
     col="blue",
     freq=FALSE)

set.seed(1)
run11Costs<-replicate (10,cpquery(bn11, event =  (TravelTimeDisc11 == 0) | (TravelTimeDisc11 == 1) , evidence = (Bridge0Road13==1),n=10000))
summary(run11Costs)
hist(run11Costs)

```



Create list of names, and also Maintenace Rate variables:

```{r chunk0002, echo = TRUE}
#Best:
# https://stackoverflow.com/questions/44676501/r-bnlearn-eval-inside-function?noredirect=1&lq=1
# https://goodscienceblog.wordpress.com/2016/12/02/a-very-useful-function-eval-parse-text-paste/
# https://stackoverflow.com/questions/16566799/change-variable-name-in-for-loop-using-r
# https://stackoverflow.com/questions/44670562/assigning-a1-1-a2-2-a3-using-for-loop-in-r?noredirect=1&lq=1
# https://stackoverflow.com/questions/68639680/accessing-dynamic-variables-in-r
Maint_rate_list<-unique(Road_cond_tables$RoadMaintenanceRate)
for (ii in 1:length(Maint_rate_list)){
  Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$RoadMaintenanceRate==Maint_rate_list[ii],"IndepenVarLvel"]
  Maint_rate_IndepenVarLvel_uniq<-unique(Maint_rate_IndepenVarLvel)
  str2<-paste(Maint_rate_list[ii],sep = "")
  assign(as.vector(paste('Maint_rate_IndepenVarLvel_prob',ii,sep="")),eval(parse(text=paste("array(c(0.6,0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq))"))) )
}
```



Create list of names, and also Roads availability and costs variables:



```{r chunk0003, echo = TRUE}
Road_dependent_var_list<-unique(Road_cond_tables$DepenVar)
for (ii in 1:length(Road_dependent_var_list)){
  Road_dependent_DepenVarLvel<-Road_cond_tables[Road_cond_tables$DepenVar==Road_dependent_var_list[ii],"DepenVarLvel"]
  Road_dependent_DepenVarLvel_uniq<-unique(Road_dependent_DepenVarLvel)
  str1<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_dependent_var_list[ii],"RoadMaintenanceRate"])
  str2<-paste(Road_dependent_var_list[ii],sep = "")
  print(str1)
  print(str2)
  
  Roaddependentprob11<-Road_cond_tables[Road_cond_tables$DepenVar==Road_dependent_var_list[ii],"CondProb"]
  assign(as.vector(paste('Road_dependent_DepenVarLvel_prob',ii,sep="")),eval(parse(text=paste("array(Roaddependentprob11, dim = c(length(Road_dependent_DepenVarLvel_uniq),length(Maint_rate_IndepenVarLvel_uniq)), dimnames = list(",str2,"= Road_dependent_DepenVarLvel_uniq,",str1,"= Maint_rate_IndepenVarLvel_uniq))"))) )
  
}
```






```{r}
get(paste('Maint_rate_IndepenVarLvel_prob',1,sep=""))
Maint_rate_IndepenVarLvel_prob3
```





```{r}
#assign(str(Maint_rate_list[ii]),"")
#parse(text=(paste(Maint_rate_list[ii],sep = "")))
#Maint_rate_IndepenVarLvel_prob<-array(c(0.6,0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(str(Maint_rate_list[ii])= Maint_rate_IndepenVarLvel_uniq))
names = c("Tom", "Bob", "Dan")
for (i in 1:length(names)){
    name = names[i]
    if (names[i] == "Bob"){
            assign(names[i],"my_name")
            print(Bob)
        }
}
for (ii in 1:length(Maint_rate_list)){
  quote(Maint_rate_list[ii])
  i7<-(text=(paste(Maint_rate_list[ii],sep = "")))
  i7
}
Maint_rate_IndepenVarLvel_prob

i <- 1
Output <- c()
Output[i] <- i+1
parse(text=(paste("Output[",i,"]*50",sep="")))
```


This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

