---
title: "Untitled"
output: html_document
date: "2023-06-29"
runtime: shiny
---

```{r setup, include=FALSE}
#update.packages(ask = FALSE)
knitr::opts_chunk$set(echo = FALSE)
#install.packages("BiocManager")
#BiocManager::install("Rgraphviz")
library("stats")
library("Rgraphviz")
#install.packages("Rgraphviz")
#BiocManager::install("Rgraphviz")
library("fitdistrplus")
library("bnlearn")
#library("bnviewer")
library("readxl")
library("hdrcde")
library(gRain)
library(stringi)
library("greekLetters")
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(DiagrammeRsvg)
library(rsvg)
#install.packages("devtools")
#devtools::install_github("robson-fernandes/bnviewer")
library(bnviewer)
```

## Simulation in Python

The Python files are provided in the folder at ...


## Reading CSV files

Here is the code for reading csv files as data-frames:


```{r chunk0001, echo = TRUE}
rm(list=ls())
#setwd("C://Users//20204066//Box//RESS-format//2022Dec10-RunFullmodel//18December2022SSBN4RYesting//")
getwd()
Road_cond_tables<-read.csv("conditional_prob_table_road_level_concate01.csv",sep = ",",2)
Subset_cond_tables<-read.csv("conditional_prob_table_road_to_subnet_level_concate01.csv",sep = ",",2)
System_cond_tables<-read.csv("conditional_prob_table_system_level.csv", sep=",",2)
```


With probability 0.6 is the first element of ordered "Maint_rate_IndepenVarLvel_uniq", and 0.4 the other element.



```{r chunk00015, echo = TRUE}
Bridge_road_list<-unique(Road_cond_tables$IndepenVar)
BNString<-""
BNString22<-""
CPString<-""
Bridge_lists_all<-list()

ii_end<-length(Bridge_road_list)
for (ii in 1:ii_end){
  if (nchar(Bridge_road_list[ii]) > 1)
    {
    BNString<-paste0(BNString, "[", paste(Bridge_road_list[ii],sep = "") ,"]")
    DepenVar<-Road_cond_tables[Road_cond_tables$IndepenVar==Bridge_road_list[ii],"DepenVar"]
    DepenVar_list<-unique(DepenVar)
    #for (jj in 1:length(DepenVar_list)){
    #  BNString22<-paste0(BNString22, "[", paste(DepenVar_list[jj],sep = "") , "|", paste(Bridge_road_list[ii],sep     # = "")  ,"]")}
    
      
    Bridge_lists_all<-append(Bridge_lists_all,Bridge_road_list[ii])
    
    
    Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$IndepenVar==Bridge_road_list[ii],"IndepenVarLvel"]
    Maint_rate_IndepenVarLvel_uniq<-sort(unique(Maint_rate_IndepenVarLvel))
    Maint_rate_IndepenVarLvel_uniq_index<-seq_along(Maint_rate_IndepenVarLvel_uniq)
    str2<-paste(Bridge_road_list[ii],sep = "")
  
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Maint_rate_IndepenVarLvel_uniq_index"))))

      
    assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(c(0.6, 0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq_index))"))) )
  
    
    
    CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))
    
    }
}



Bridge_road_list<-unique(Road_cond_tables$IndepenVar1)
ii_end<-length(Bridge_road_list)
for (ii in 1:ii_end){
  if (nchar(Bridge_road_list[ii]) > 1)
    {
    BNString<-paste0(BNString, "[", paste(Bridge_road_list[ii],sep = "") ,"]")
    DepenVar<-Road_cond_tables[Road_cond_tables$IndepenVar1==Bridge_road_list[ii],"DepenVar"]
    DepenVar_list<-unique(DepenVar)

    
    
    
    Bridge_lists_all<-append(Bridge_lists_all,Bridge_road_list[ii])
    
    
    Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$IndepenVar1==Bridge_road_list[ii],"IndepenVar1Lvel"]
    Maint_rate_IndepenVarLvel_uniq<-sort(unique(Maint_rate_IndepenVarLvel))
    Maint_rate_IndepenVarLvel_uniq_index<-seq_along(Maint_rate_IndepenVarLvel_uniq)
    str2<-paste(Bridge_road_list[ii],sep = "")
  
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Maint_rate_IndepenVarLvel_uniq_index"))))
  
    assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(c(0.6, 0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq_index))"))) )

    

    
    CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))

              
    }
}





Bridge_road_list<-unique(Road_cond_tables$IndepenVar2)
ii_end<-length(Bridge_road_list)
for (ii in 1:ii_end){
  if (nchar(Bridge_road_list[ii]) > 1)
    {
    BNString<-paste0(BNString, "[", paste(Bridge_road_list[ii],sep = "") ,"]")
    DepenVar<-Road_cond_tables[Road_cond_tables$IndepenVar2==Bridge_road_list[ii],"DepenVar"]
    DepenVar_list<-unique(DepenVar)

    
    
    Bridge_lists_all<-append(Bridge_lists_all,Bridge_road_list[ii])
    
    
    Maint_rate_IndepenVarLvel<-Road_cond_tables[Road_cond_tables$IndepenVar2==Bridge_road_list[ii],"IndepenVar2Lvel"]
    Maint_rate_IndepenVarLvel_uniq<-sort(unique(Maint_rate_IndepenVarLvel))
    Maint_rate_IndepenVarLvel_uniq_index<-seq_along(Maint_rate_IndepenVarLvel_uniq)
    str2<-paste(Bridge_road_list[ii],sep = "")
  
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Maint_rate_IndepenVarLvel_uniq_index"))))
  
    assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(c(0.6, 0.4), dim = length(Maint_rate_IndepenVarLvel_uniq), dimnames = list(",str2,"= Maint_rate_IndepenVarLvel_uniq_index))"))) )
    # array(Maint_rate_IndepenVarLvel_uniq 

    CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))
        
      
    }
}









```



## Continue

```{r chunk00016, echo = TRUE}



Raod_list_BNString<-unique(Road_cond_tables$DepenVar)
for (ii in 1:length(Raod_list_BNString)){
    IndepenVar<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Raod_list_BNString[ii],"IndepenVar"])
    IndepenVar1<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Raod_list_BNString[ii],"IndepenVar1"])
    IndepenVar2<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Raod_list_BNString[ii],"IndepenVar2"])

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Raod_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1){  
    BNString22<-paste0(BNString22, "[", paste(Raod_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,sep = "")  ,"]")
    
    }
    else {
    BNString22<-paste0(BNString22, "[", paste(Raod_list_BNString[ii],sep = "") , "|", paste(IndepenVar,sep = "")  ,"]")
      
    }
  }


Road_list<-unique(Road_cond_tables$DepenVar)
Road_lists_all<-list()


for (ii in 1:length(Road_list)){
  if (nchar(Road_list[ii]) > 1)
    {

    #BNString<-paste0(BNString, "[", paste(Road_list[ii],sep = "") ,"]")
    Road_lists_all<-append(Road_lists_all,Road_list[ii])
    
    
    Road_cond_prob<-Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"CondProb"]
    Road_levels_list<-Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"DepenVarLvel"]
    Road_levels_list_index<-seq_along(unique(Road_levels_list))
    Road_levels_list_num<-length(unique(Road_levels_list))
    

    IndepenVar<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar"])
    IndepenVar_uniq_num<-length(unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVarLvel"]))
    IndepenVar1<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar1"])
    IndepenVar1_uniq_num<-length(unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar1Lvel"]))
    IndepenVar2<-unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar2"])
    IndepenVar2_uniq_num<-length(unique(Road_cond_tables[Road_cond_tables$DepenVar==Road_list[ii],"IndepenVar2Lvel"]))

        
    str2<-paste(Road_list[ii],sep = "")
    str3<-paste(IndepenVar,"=",IndepenVar,"_range",sep = "")
    str4<-paste(IndepenVar1,"=",IndepenVar1,"_range",sep = "")
    str5<-paste(IndepenVar2,"=",IndepenVar2,"_range",sep = "")

    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Road_levels_list_index"))))
    
    #cat(IndepenVar2_uniq_num,'IndepenVar2_uniq_num')

        

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){

      # rr<-paste("arrayRoad_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,str4,str5,"))")
      #print(rr)
      
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Road_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,",",str4,",",str5,"))"))) )
    }
        

    else if (nchar(IndepenVar1) > 1){

      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Road_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,",",str4,"))"))) )
    }
     else {
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Road_cond_prob, dim = c(Road_levels_list_num,IndepenVar_uniq_num ), dimnames = list(",str2,"= Road_levels_list_index,",str3,"))"))) )
       
     }   

    if (ii <=length(Road_list) ){
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))}
    else {
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob',sep=""))
    }
    
    }
}




```


Read and create subnet file..

```{r chunk00017, echo = TRUE}
BNString22
Subnet_list_BNString<-unique(Subset_cond_tables$DepenVar)
for (ii in 1:length(Subnet_list_BNString)){

    IndepenVar<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar"])
    IndepenVar1<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar1"])
    IndepenVar2<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar2"])
    IndepenVar3<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list_BNString[ii],"IndepenVar3"])

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1  & nchar(IndepenVar3) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,":",IndepenVar3,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1){  
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,sep = "")  ,"]")
    
    }
    else {
    BNString22<-paste0(BNString22, "[", paste(Subnet_list_BNString[ii],sep = "") , "|", paste(IndepenVar,sep = "")  ,"]")
      
    }
  }




Subnet_list<-unique(Subset_cond_tables$DepenVar)
Subnet_lists_all<-list()



for (ii in 1:length(Subnet_list)){
  if (nchar(Subnet_list[ii]) > 1  )
    {

    #BNString<-paste0(BNString, "[", paste(Road_list[ii],sep = "") ,"]")
    Subnet_lists_all<-append(Subnet_lists_all,Subnet_list[ii])
    
    
    Subnet_cond_prob<-Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"CondProb"]
    Subnet_levels_list<-Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"DepenVarLvel"]
    Subnet_levels_list_index<-seq_along(unique(Subnet_levels_list))
    Subnet_levels_list_num<-length(unique(Subnet_levels_list))
    

    

    IndepenVar<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar"])
    IndepenVar_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVarLvel"]))
    IndepenVar1<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar1"])
    IndepenVar1_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar1Lvel"]))
    IndepenVar2<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar2"])
    IndepenVar2_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar2Lvel"]))
    IndepenVar3<-unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar3"])
    IndepenVar3_uniq_num<-length(unique(Subset_cond_tables[Subset_cond_tables$DepenVar==Subnet_list[ii],"IndepenVar3Lvel"]))

        
    str2<-paste(Subnet_list[ii],sep = "")
    str3<-paste(IndepenVar,"=",IndepenVar,"_range",sep = "")
    str4<-paste(IndepenVar1,"=",IndepenVar1,"_range",sep = "")
    str5<-paste(IndepenVar2,"=",IndepenVar2,"_range",sep = "")
    str6<-paste(IndepenVar3,"=",IndepenVar3,"_range",sep = "")
    assign(as.vector(paste(str2,"_range",sep="")),eval(parse(text=paste("Subnet_levels_list_index"))))

    #cat("    %%%%%%%%%%  ",ii)
    #cat("::::", IndepenVar_uniq_num, IndepenVar1_uniq_num, Subnet_levels_list_num)
    #cat("uuuuuuuuuuu")
    

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1 & nchar(IndepenVar3) > 1){

     # rr<-paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,",",str6,"))")
      # print(rr)

            
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num,IndepenVar3_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,",",str6,"))"))) )
    }

    else if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){

      # rr<-paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,"))")
      # print(rr)

            
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,",",str5,"))"))) )
    }
        

    else if (nchar(IndepenVar1) > 1){

      #rr<-paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,"))")
      #print(rr)
      
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,",",str4,"))"))) )
    }
     else {
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(Subnet_cond_prob, dim = c(Subnet_levels_list_num,IndepenVar_uniq_num ), dimnames = list(",str2,"= Subnet_levels_list_index,",str3,"))"))) )
       
     }   

    if (ii <=length(Subnet_list) ){
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))}
    else {
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob',sep=""))
    }
    
    }
}




```



system nodes and conditional probs

```{r chunk00018, echo = TRUE}

Sys_list_BNString<-unique(System_cond_tables$DepenVar)

for (ii in 1:length(Sys_list_BNString)){
    IndepenVar<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar"])
    IndepenVar1<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar1"])
    IndepenVar2<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar2"])
    IndepenVar3<-unique(System_cond_tables[System_cond_tables$DepenVar==Sys_list_BNString[ii],"IndepenVar3"])

    if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1  & nchar(IndepenVar3) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,":",IndepenVar3,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1 & nchar(IndepenVar2) > 1){    
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,":",IndepenVar2,sep = "")  ,"]")
    }
    else if (nchar(IndepenVar1) > 1){  
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,":",IndepenVar1,sep = "")  ,"]")
    
    }
    else {
    BNString22<-paste0(BNString22, "[", paste(Sys_list_BNString[ii],sep = "") , "|", paste(IndepenVar,sep = "")  ,"]")
      
    }
  }



System_var_list<-unique(System_cond_tables$DepenVar)
System_var_lists_all<-list()


for (ii in 1:length(System_var_list)){
  if (nchar(System_var_list[ii]) > 1  )
    {

    #BNString<-paste0(BNString, "[", paste(Road_list[ii],sep = "") ,"]")
    System_var_lists_all<-append(System_var_lists_all,System_var_list[ii])
    
    
    System_cond_prob<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"CondProb"]
    System_var_levels_list<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"DepenVarLvel"]
    System_var_levels_list_index<-seq_along(unique(System_var_levels_list))
    System_var_levels_list_num<-length(unique(System_var_levels_list))
    
    IndepenVar_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVarLvel"]))
    IndepenVar1_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar1Lvel"]))
    IndepenVar2_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar2Lvel"]))
    IndepenVar3_uniq_num<-length(unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar3Lvel"]))

    

    IndepenVar<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar"])
    IndepenVar1<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar1"])
    IndepenVar2<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar2"])
    IndepenVar3<-unique(System_cond_tables[System_cond_tables$DepenVar==System_var_list[ii],"IndepenVar3"])

        
    str2<-paste(System_var_list[ii],sep = "")
    str3<-paste(IndepenVar,"=",IndepenVar,"_range",sep = "")
    str4<-paste(IndepenVar1,"=",IndepenVar1,"_range",sep = "")
    str5<-paste(IndepenVar2,"=",IndepenVar2,"_range",sep = "")
    str6<-paste(IndepenVar3,"=",IndepenVar3,"_range",sep = "")

    #cat("    %%%%%%%%%%  ",ii)
    #cat("::::", IndepenVar_uniq_num, IndepenVar1_uniq_num, Subnet_levels_list_num)
    #cat("uuuuuuuuuuu")
    


    rr<-paste("array(System_cond_tables, dim = c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num ), dimnames = list(",str2,"= System_var_levels_list_index,",str3,",",str4,",",str5,",",str6,"))")
    print(rr)

            
      assign(as.vector(paste(str2,'_prob',sep="")),eval(parse(text=paste("array(System_cond_prob, dim = c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num,IndepenVar2_uniq_num,IndepenVar3_uniq_num ), dimnames = list(",str2,"= System_var_levels_list_index,",str3,",",str4,",",str5,",",str6,"))"))) )

    if (ii <length(System_var_list) ){
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob,',sep=""))}
    else {
      CPString<-paste0(CPString,str2,"=",paste(str2,'_prob',sep=""))
    }
    
    }
}


# System_cond_prob<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[1],"CondProb"]
# System_var_levels_list<-System_cond_tables[System_cond_tables$DepenVar==System_var_list[1],"DepenVarLvel"]
# System_var_levels_list_index<-seq_along(unique(System_var_levels_list))
# System_var_levels_list_num<-length(unique(System_var_levels_list))
# 
# System_var_levels_list_index
# c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num )
# list( TotalCostDisc11 = System_var_levels_list_index, Subnet0Costs=Subnet0Costs_range , Subnet1Costs=Subnet1Costs_range , Subnet2Costs=Subnet2Costs_range , Subnet3Costs=Subnet3Costs_range )
# tte<-array(System_cond_tables, dim = c(System_var_levels_list_num,IndepenVar_uniq_num,IndepenVar1_uniq_num, IndepenVar2_uniq_num, IndepenVar3_uniq_num ), dimnames = list( TotalCostDisc11 = System_var_levels_list_index, Subnet0Costs=Subnet0Costs_range , Subnet1Costs=Subnet1Costs_range , Subnet2Costs=Subnet2Costs_range , Subnet3Costs=Subnet3Costs_range ))


```




Creat BN model

```{r chunk00019, echo=FALSE, fig.asp=.62, fig.width=55,  dev='png', fig.show='hide'}
CPString#<-"Bridge0Road13=Bridge0Road13_prob,Road13Avail=Road13Avail_prob"
assign(as.vector(paste('cpt',sep="")),eval(parse(text=paste("list(",CPString,")"))) )
cpt
BNString22

#BNStringAll<-paste0("[Bridge0Road13]",BNString22,"")
BNStringAll<-paste0(BNString,BNString22,"")
BNStringAll
BNLayerOneTime = model2network(BNStringAll)
cpt


bn11 = custom.fit(BNLayerOneTime, cpt)
bn.to.igraph(bn11)


#data("alarm")
#bayesianNetwork = hc(alarm)

graphics.off()
dev.new()
#par("mar")
par(mar=c(0.1,0.1,0.1,0.1))#par(mar = c(1, 1, 1, 1))
#par(mfcol=c(10,3),mai=c(0.5,0.5,0.5,0))
#par(cex=0.05)#,mai=c(0.1,0.1,0.1,0.1))

#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")

graphviz.chart(bn11, type = "barprob", scale = c(8.8, 8.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "lightskyblue")


reso <- 500
#length <- 2*reso/72
#png("C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc8\\MarginalDisFromRV012.png",10, 8, units="in",res=1000) #,height=length,width=length)

pdf("C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc5\\MarginalDisFromRV012.pdf",width = 28, height = 28) #,height=length,width=length)


#graphviz.chart(bn11,  type = "barprob", layout = "dot")
#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")
graphviz.chart(bn11, type = "barprob", scale = c(8.8, 8.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "lightskyblue")


#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")
invisible(dev.off())
dev.set(dev.next())

```



```{r chunk000221, echo=FALSE, fig.asp=.62, fig.width=55,  dev='png', fig.show='hide'}
#(TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 2)
# "C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc5\\"
# Conditional_prob("(TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 2)","C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc5\\", "Time12")
Conditional_prob <- function(cond11, path_string, file_extensions,max_i_index,min_i_index,base_independent_var){

  set.seed(1)
  final_max_comb <-""
  final_min_comb<-""
  rr<-combn(seq.int(20),5)
  ave_list11 <- rep(0, 2) 
  max_ave<-0
  min_ave<-1
  if (max_i_index==0){
  end_index<-length(rr)-50
  for(i in 1:end_index) {  
  
  bridge1_str<-(Bridge_lists_all[[rr[1,i]]])
  bridge2_str<-(Bridge_lists_all[[rr[2,i]]])
  bridge3_str<-(Bridge_lists_all[[rr[3,i]]])
  bridge4_str<-(Bridge_lists_all[[rr[4,i]]])
  bridge5_str<-(Bridge_lists_all[[rr[5,i]]])
  
  assign(as.vector(paste('result_inf1',sep="")),eval(parse(text=paste("replicate (500,cpquery(bn11, event =  ",cond11,"  , evidence = ( (",bridge1_str," == 2) & (",bridge2_str," == 2) & (",bridge3_str," == 2) & (",bridge4_str," == 2) & (",bridge5_str," == 2)),n=5000))"))) )
  
  
  
  # result_inf1
  #result_inf<-unname(result_inf1)
  #mean11<-result_inf[[2]]
  mean11<-unname(summary(result_inf1)[4])
  ave_list11[[length(ave_list11) + 1]] <-mean11
  if (max_ave<mean11){
    max_i_index<-i
    final_max_comb<-paste(bridge1_str,bridge2_str,bridge3_str,bridge4_str,bridge5_str)
    max_ave<-mean11
    capture.output(paste(final_max_comb,paste(max_ave)), file =paste(path_string,"final_max_comb",file_extensions, ".txt")) 
    ggplot() + geom_histogram(aes(result_inf1), bins = 100)
    ggsave(path = path_string,filename=paste("Max_i_conditional_sample",file_extensions,".png"))
}
  
  if (min_ave>mean11){
    min_i_index<-i
    final_min_comb<-paste(bridge1_str,bridge2_str,bridge3_str,bridge4_str, bridge5_str)
    min_ave<-mean11
    capture.output(paste(final_min_comb,paste(min_ave)), file =paste(path_string,"final_min_comb",file_extensions, ".txt")) 
    ggplot() + geom_histogram(aes(result_inf1), bins = 100)
    ggsave(path = path_string,filename=paste("Min_i_conditional_sample",file_extensions,".png"))
  }
  if (i %%500==0){
    print(paste("max",final_max_comb,max_i_index,max_ave))
    print(paste("min",final_min_comb,min_i_index,min_ave))
  }
  
  
  }
  }
  if (max_i_index>0){
  i<-max_i_index
  bridge1_str<-(Bridge_lists_all[[rr[1,i]]])
  bridge2_str<-(Bridge_lists_all[[rr[2,i]]])
  bridge3_str<-(Bridge_lists_all[[rr[3,i]]])
  bridge4_str<-(Bridge_lists_all[[rr[4,i]]])
  bridge5_str<-(Bridge_lists_all[[rr[5,i]]])
  final_max_comb<-paste(bridge1_str,bridge2_str,bridge3_str,bridge4_str,bridge5_str)
  
  assign(as.vector(paste('result_inf1',sep="")),eval(parse(text=paste("replicate (500,cpquery(bn11, event =  ",cond11,"  , evidence = ( (",bridge1_str," == ",str(base_independent_var),") & (",bridge2_str," == ",str(base_independent_var),") & (",bridge3_str," == ",str(base_independent_var),") & (",bridge4_str," == ",str(base_independent_var),") & (",bridge5_str," == ",str(base_independent_var),")),n=5000))"))) )
  result_inf<-unname(result_inf1)
  max_ave<-result_inf[[2]]
  
  ggplot() + geom_histogram(aes(result_inf1), bins = 100)
  ggplot() + geom_histogram(aes(result_inf1), bins = 100)
  ggsave(path = path_string,filename=paste("Max_i_conditional",file_extensions,".png"))
  
  
  
  
  i<-min_i_index
  bridge1_str<-(Bridge_lists_all[[rr[1,i]]])
  bridge2_str<-(Bridge_lists_all[[rr[2,i]]])
  bridge3_str<-(Bridge_lists_all[[rr[3,i]]])
  bridge4_str<-(Bridge_lists_all[[rr[4,i]]])
  bridge5_str<-(Bridge_lists_all[[rr[5,i]]])
  final_min_comb<-paste(bridge1_str,bridge2_str,bridge3_str,bridge4_str, bridge5_str)
  
  assign(as.vector(paste('result_inf1',sep="")),eval(parse(text=paste("replicate (500,cpquery(bn11, event =  ",cond11,"   , evidence = ( (",bridge1_str," == 1) & (",bridge2_str," == 1) & (",bridge3_str," == 1) & (",bridge4_str," == 1) & (",bridge5_str,"==1 )),n=5000))"))) )
  ggplot() + geom_histogram(aes(result_inf1), bins = 100)
  ggsave(path = path_string,filename=paste("Min_i_conditional",file_extensions,".png"))
  
  result_inf<-unname(result_inf1)
  min_ave<-result_inf[[2]]
capture.output(paste(final_max_comb,paste(max_ave)), file =paste(path_string,"final_max_comb",file_extensions, ".txt")) 
capture.output(paste(final_min_comb,paste(min_ave)), file =paste(path_string,"final_min_comb",file_extensions, ".txt")) 
}
#return(c(final_max_comb,final_min_comb))  
}

Min_max_index<-Conditional_prob("(TravelTimeDisc11 == 2) |(TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 0)","C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc8\\", "Time012",0,0,1)

Min_max_index<-Conditional_prob("(TravelTimeDisc11 == 0) | (TravelTimeDisc11 == 0)","C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc8\\", "Time0",0,0,1)

Min_max_index<-Conditional_prob("(TotalCostDisc11 == 0) | (TotalCostDisc11 == 3)","C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc8\\", "Cost03",0,0,1)

Min_max_index<-Conditional_prob("(TotalCostDisc11 == 0) | (TotalCostDisc11 == 1)","C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc5\\", "Cost01",0,0,1)


Min_max_index<-Conditional_prob("(TotalCostDisc11 == 0) | (TotalCostDisc11 == 3)","C:\\Users\\Mohsen\\Documents\\PythonProjects\\Opac\\OutputResults29June2023V75disc8\\", "Cost03Base2",0,0,0)


```




```{r chunk000222, echo=FALSE, fig.asp=.62, fig.width=55,  dev='png', fig.show='hide'}




```



# till here




```{r chunk00059, echo=FALSE, fig.asp=.62, fig.width=55,  dev='png', fig.show='hide'}

viewer(BNLayerOneTime,
	bayesianNetwork.width = "150%",
	bayesianNetwork.height = "80vh",
	bayesianNetwork.layout = "layout_components",
	bayesianNetwork.title="Los Angeles County",
	bayesianNetwork.subtitle = "Bridge Network",
	bayesianNetwork.footer = "Fig. 1 - Layout with Sugiyama",
	edges.width = 4,
	node.shape = "ellipse"
)


set.seed(1)

assign(as.vector(paste("Bridge1",sep="")),eval(parse(text=paste("Bridge_lists_all[[1]]"))))

result_inf1<-replicate (5,cpquery(bn11, event =  (TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 0)  , evidence = ( (Bridge2Road57 == 1) & (Bridge0Road50 == 1) & (Bridge0Road57 == 1) & (Bridge0Road63 == 1)),n=10000))

unname(summary(result_inf1)[4])
names(summary(result_inf1))[4]
bridge1_str<-(Bridge_lists_all[[1]])
assign(as.vector(paste('result_inf1',sep="")),eval(parse(text=paste("replicate (5,cpquery(bn11, event =  (TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 0)  , evidence = ( (",bridge1_str," == 1) & (Bridge0Road13 == 1) & (Bridge0Road57 == 1) & (Bridge0Road63 == 1)),n=10000))"))) )



result_inf1


result_inf1<-replicate (5,cpquery(bn11, event =  (TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 0)  , evidence = ( (Bridge0Road13 == 1) & (Bridge0Road24 == 1) & (Bridge0Road57 == 1) & (Bridge0Road63 == 1)),n=10000))
summary(result_inf1)
result_inf1 <- as.numeric(result_inf1)
result_inf<-unname(result_inf1)
result_inf[[0]]
result_inf1

hist(result_inf1)
result_inf1
names(result_inf1)
result_inf[[3]]

ggplot() + geom_histogram(aes(result_inf1), bins = 15)




result_inf1<-replicate (100,cpquery(bn11, event =  (TravelTimeDisc11 == 1) | (TravelTimeDisc11 == 0)  , evidence = ( (Bridge0Road13 == 2) & (Bridge0Road49 == 2) & (Bridge0Road57 == 2) & (Bridge0Road63 == 2)),n=10000))
summary(result_inf1)
result_inf1 <- as.numeric(result_inf1)
ggplot() + geom_histogram(aes(result_inf1))



```

## Here till hereeeeeeeeeeeeeeeeeeeee


```{r}

#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")
#graphviz.chart(bn11,  type = "barprob", layout = "dot")
#par(mar=rep(0,4))
graphics.off()
dev.new()
#par("mar")
par(mar=c(0.1,0.1,0.1,0.1))#par(mar = c(1, 1, 1, 1))
#par(mfcol=c(10,3),mai=c(0.5,0.5,0.5,0))
#par(cex=0.05)#,mai=c(0.1,0.1,0.1,0.1))

#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")

graphviz.chart(bn11, type = "barprob", grid = TRUE, bar.col = "darkgreen",strip.bg = "lightskyblue")


reso <- 500
#length <- 2*reso/72
png("MarginalDisFromRV011.png",10, 8, units="in",res=1000) #,height=length,width=length)

#graphviz.chart(bn11,  type = "barprob", layout = "dot")
#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")
graphviz.chart(bn11, type = "barprob", grid = TRUE, bar.col = "darkgreen",strip.bg = "lightskyblue")


#graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")
invisible(dev.off())
dev.set(dev.next())


#http://robsonfernandes.net/bnviewer/
# https://cran.r-project.org/web/packages/bnviewer/bnviewer.pdf



graphviz.chart(bn11, type = "barprob",scale = c(2.8, 2.5), grid = TRUE, bar.col = "darkgreen",strip.bg = "white")

graphviz.plot(bn11, layout = "fdp") #circo


bn.fit.barchart(bn11$Road57Costs, main = "Subnet3Costs",
                xlab = "Pr(Subnet3Costs |..)", ylab = "")

graphviz.plot(bn11, shape = "ellipse")

par(mar=rep(0,4))
graphviz.chart(bn11, type = "barprob", layout = "dot")
par(cex=0.05)
graphviz.chart(bn11,  type = "barprob", layout = "dot")
typeof(gg)
export_graph(gg,
file_name = "29JuneBN11.png",
file_type = "png")
#https://www.bnlearn.com/examples/graphviz-plot/
export_graph(ToDiagrammeRGraph(gg), "export.pdf")
#Distribution here 


```


## Here 1

```{r fig3, fig.width = 55, fig.asp = .62}
#https://github.com/robson-fernandes/bnviewer
packageVersion("rlang") # ‘1.0.6’
devtools::install_github("r-lib/rlang")
packageVersion("rlang") # ‘1.1.0.9000’
install.packages("rlang", version="1.1.0")

#update.packages(ask = FALSE)
install.packages("devtools")
devtools::install_github("robson-fernandes/bnviewer")
library(bnviewer)
par(cex=0.05)
graphviz.chart(bn11, type = "barprob")
```



